The Chemistry Development Kit (CDK). 3. Atom typing, Rendering, Molecular Formula, and Substructure Searching

### 2016-08-11 article.tex
Added Chris Evelo, group leader of Egon
Added ChemViz2 (closes #20)

\author[
   addressref={um},                   % id's of addresses, e.g. {aff1,aff2}
   %corref={aff1},                       % id of corresponding address, if any
   %noteref={n1},                        % id's of article notes, if any
   email={egon.willighagen@maastrichtuniversity.nl}   % email address
]{\inits{ELW}\fnm{Egon L} \snm{Willighagen}}
\author[
   addressref={aff2},
   email={john@nextmovesoftware.com}
]{\inits{JWM}\fnm{John W} \snm{May}}
\author[
   addressref={uppsala},
   email={jonathan.alvarsson@farmbio.uu.se}
]{\inits{JA}\fnm{Jonathan} \snm{Alvarsson}}
\author[
   addressref={uppsala},
   email={berg.arvid@gmail.com}
]{\inits{AB}\fnm{Arvid} \snm{Berg}}
\author[
   addressref={idea},
   email={jeliazkova.nina@gmail.com}
]{\inits{NJ}\fnm{Nina} \snm{Jeliazkova}}
\author[
   addressref={wi_mit},
   email={pluskal@wi.mit.edu}
]{\inits{TP}\fnm{Tomáš}~\snm{Pluskal}}
\author[
   addressref={???},
   email={miguelrojasch@googlemail.com}
]{\inits{MRJ}\fnm{Miguel}~\snm{Rojas-Cherto}}
\author[
   addressref={uppsala},
   email={ola.spjuth@farmbio.uu.se}
]{\inits{OS}\fnm{Ola} \snm{Spjuth}}
\author[
   addressref={???},
   email={gilleain.torrance@gmail.com}
]{\inits{GT}\fnm{Gilleain} \snm{Torrance}}
\author[
   addressref={nih},
   email={guhar@mail.nih.gov}
]{\inits{RG}\fnm{Rajarshi} \snm{Guha}}
\author[
   addressref={ebi},
   email={steinbeck@ebi.ac.uk}
]{\inits{CS}\fnm{Christoph}~\snm{Steinbeck}}

@@

Open Source cheminformatics has made significant steps forward recently~\cite{OBoyle2011}.
The Chemistry Development Kit (CDK) is one of the tools under the Blue Obelisk wings,
and previously documented version have been widely adopted~\cite{Steinbeck2003,Steinbeck2006}.
For example, new tools expose CDK functionality in larger platforms such as Cinfony~\cite{OBoyle2008},
rcdk~\cite{Guha2007}, and plugins for Taverna~\cite{Truszkowski2011},
KNIME~\cite{Beisken2013}, and LICSS for Excel~\cite{Lawson2012}.
Furthermore, projects with specific functionality have emerged building on the CDK, including
jCompoundMapper~\cite{Hinselmann2011}, ScaffoldHunter~\cite{wetzel2009interactive}, OMG~\cite{Peironcely2012},
Padel~\cite{yap2011padel}, AMBIT-SMARTS~\cite{jeliazkova2011ambitsmarts}, AMBIT-Tautomer~\cite{kochev2013ambit},
and SMSD~\cite{Rahman2009,Rahman2014}. Other tools used previous versions already, and follow
newer releases of the CDK, such as Bioclipse~\cite{spjuth2007bioclipse,
spjuth2009bioclipse} and AMBIT~\cite{jeliazkova2011ambit}. While the above
tools suggest that the CDK is primarily used to create general tools, it is
important to note that it is also used to solve specific questions, like finding
the maximally bridging rings in chemical structures~\cite{Marth2015}.

>>>>

\author[
   addressref={um},                   % id's of addresses, e.g. {aff1,aff2}
   %corref={aff1},                       % id of corresponding address, if any
   %noteref={n1},                        % id's of article notes, if any
   email={egon.willighagen@maastrichtuniversity.nl}   % email address
]{\inits{ELW}\fnm{Egon L} \snm{Willighagen}}
\author[
   addressref={aff2},
   email={john@nextmovesoftware.com}
]{\inits{JWM}\fnm{John W} \snm{May}}
\author[
   addressref={uppsala},
   email={jonathan.alvarsson@farmbio.uu.se}
]{\inits{JA}\fnm{Jonathan} \snm{Alvarsson}}
\author[
   addressref={uppsala},
   email={berg.arvid@gmail.com}
]{\inits{AB}\fnm{Arvid} \snm{Berg}}
\author[
   addressref={idea},
   email={jeliazkova.nina@gmail.com}
]{\inits{NJ}\fnm{Nina} \snm{Jeliazkova}}
\author[
   addressref={wi_mit},
   email={pluskal@wi.mit.edu}
]{\inits{TP}\fnm{Tomáš}~\snm{Pluskal}}
\author[
   addressref={???},
   email={miguelrojasch@googlemail.com}
]{\inits{MRJ}\fnm{Miguel}~\snm{Rojas-Cherto}}
\author[
   addressref={uppsala},
   email={ola.spjuth@farmbio.uu.se}
]{\inits{OS}\fnm{Ola} \snm{Spjuth}}
\author[
   addressref={???},
   email={gilleain.torrance@gmail.com}
]{\inits{GT}\fnm{Gilleain} \snm{Torrance}}
\author[
   addressref={um},
   email={chris.evelo@maastrichtuniversity.nl}
]{\inits{CTE}\fnm{Chris T} \snm{Evelo}}
\author[
   addressref={nih},
   email={guhar@mail.nih.gov}
]{\inits{RG}\fnm{Rajarshi} \snm{Guha}}
\author[
   addressref={ebi},
   email={steinbeck@ebi.ac.uk}
]{\inits{CS}\fnm{Christoph}~\snm{Steinbeck}}

@@

Open Source cheminformatics has made significant steps forward recently~\cite{OBoyle2011}.
The Chemistry Development Kit (CDK) is one of the tools under the Blue Obelisk wings,
and previously documented version have been widely adopted~\cite{Steinbeck2003,Steinbeck2006}.
For example, new tools expose CDK functionality in larger platforms such as Cinfony~\cite{OBoyle2008},
rcdk~\cite{Guha2007}, and plugins for Taverna~\cite{Truszkowski2011},
KNIME~\cite{Beisken2013}, ChemViz2 for Cytoscape~\cite{ChemViz2}, and LICSS for
Microsoft Excel~\cite{Lawson2012}.
Furthermore, projects with specific functionality have emerged building on the CDK, including
jCompoundMapper~\cite{Hinselmann2011}, ScaffoldHunter~\cite{wetzel2009interactive}, OMG~\cite{Peironcely2012},
Padel~\cite{yap2011padel}, AMBIT-SMARTS~\cite{jeliazkova2011ambitsmarts}, AMBIT-Tautomer~\cite{kochev2013ambit},
and SMSD~\cite{Rahman2009,Rahman2014}. Other tools used previous versions already, and follow
newer releases of the CDK, such as Bioclipse~\cite{spjuth2007bioclipse,
spjuth2009bioclipse} and AMBIT~\cite{jeliazkova2011ambit}. While the above
tools suggest that the CDK is primarily used to create general tools, it is
important to note that it is also used to solve specific questions, like finding
the maximally bridging rings in chemical structures~\cite{Marth2015}.
